Method quality control

### 2018-01-30 analysis/analyses/4-method_characterisation/2_quality_control.Rmd
added datasets table, update to methods section

>>>>

Table for the different checks
```{r, results="asis"}
library(kableExtra)
table <- checks %>% 
  mutate(
    weight = cell_spec(
      pritt("<span style='display: none;'>{question_id}</span> {weight}"), # add an invisible grouping indicator
      background = spec_color(weight, end=0.9,option="A",direction=-1),
      escape=FALSE,
      color="white"
    )
  ) %>%
  mutate(
    references = references %>% 
      gsub(",", "; ", .) %>% 
      {ifelse(!is.na(.), pritt("[{.}]"), "")} %>%
      {pritt("<span style='display: none;'>{question_id}</span> {.}")} # add an invisible grouping indicator
  ) %>% 
  select(question, weight, references, score, scoring, !!qc_applications$application) %>% 
  mutate_at(vars(!!qc_applications$application), ~ifelse(., "✓", "")) %>% 
  rename_all(label_long) %>% 
  knitr::kable("html", escape=FALSE) %>% 
  kable_styling(bootstrap_options = "striped") %>% 
  collapse_rows(columns=1:3)

for (category in unique(checks$category)) {
  color <- qc_categories %>% filter(category == !!category) %>% pull(color)
  table <- table %>% 
    group_rows(
      label_long(category), 
      min(which(checks$category == category)), 
      max(which(checks$category == category)),
      label_row_css = pritt("background-color: {color}; color: #fff;")
  )
}

table %>% write_rds(figure_file("qc_checks.rds"))

table
```
